---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina = 2
)
```

`hyphenatr` : HYPHENATE ALL THE THINGS

extra dictionaries from <http://www.textcontrol.com/en_US/downloads/dictionaries/>

more docs coming, i just needed to get this into gh

The following functions are implemented:

The following data sets are included:

### News

- Version  released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/hyphenatr")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(hyphenatr)

# current verison
packageVersion("hyphenatr")

```

### Test Results

```{r}
library(hyphenatr)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
