---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina = 2
)
```

`hyphenatr` : HYPHENATE ALL THE THINGS

At the moment, this requires <https://github.com/hunspell/hyphen> to  be installed on the local system first. Am working to get it to ship with the package.

Support for extra hyphenation rules from <http://www.textcontrol.com/en_US/downloads/dictionaries/> coming soon.

The following functions are implemented:

- `hyphenate` : hyphenate a vector of words, returning either a vector with hyphens (or specified strings) or a list of hypenated word components.

### News

- Version 0.1.0.9000 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/hyphenatr")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(hyphenatr)
library(jsonlite)
library(microbenchmark)

# current verison
packageVersion("hyphenatr")

# test word list (10K words)
dat <- readLines(system.file("extdata/top10000en.txt", package="hyphenatr"))

microbenchmark(out1 <- hyphenate(dat))

out1[500:550]

microbenchmark(out2 <- hyphenate(dat, simplify=FALSE))

jsonlite::toJSON(out2[530:540], pretty=TRUE)

microbenchmark(out3 <- hyphenate(dat, simplify="-"))

out3[500:550]

microbenchmark(out4 <- hyphenate(dat, simplify="&shy;"))

out4[500:550]
```

### Test Results

```{r}
library(hyphenatr)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
